An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-03-14 Paper.tex
Add structural break to MC
Change the first monte carlo to add a structural break set of simulation; they
reflect really well on my statistic.  I also removed the second set of simulations
from the paper (the code is still there, but it's off the dependency path for the
pdf paper) since the first sims are so awesome.

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
\usepackage[T1]{fontenc}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round,comma]{natbib}
\usepackage[margin=1.25in]{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/mcDef}
\input{tex/ap}

@@

The next section presents our new statistics and Section~\ref{sec:1b}
our block bootstrap result.  Section~\ref{sec:2} presents two
simulations that compare our pairwise \oos\ test to \poscw\ original
statistic.  Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability. Section~\ref{sec:4} concludes.

@@

\section{Monte Carlo Results}\label{sec:2}
I will conduct two brief Monte Carlo experiments to demonstrate that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they
study.\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \textsc{MASS}
  \citep[7.3-22]{VeR:02}, xtable \citep[version 1.6-0]{Dah:09}, and
  dbframe \citep[version 0.2.7]{Cal:10b} packages.}

The first \dgp\ has three different parametrizations; one to study the
tests' size, one to study power under stationarity, and one to study
power if there is a single break in the relationship between the
target and predictors.  The \dgp\ is:
\begin{align*}
  y_t &= 0.5 + \gamma^{*}_t z_{t-1} + e_t &
  \gamma^{*}_t &=
  \begin{cases}
    0    & \text{size simulations} \\
    0.35 & \text{power (stable)} \\
    0    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
    0.70 & t > \tfrac{T}{2} \quad \text{power (break)}
  \end{cases}\\\nonumber
  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
  \end{pmatrix}
   , \begin{pmatrix} 18 & -
    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg).
\end{align*}
Both models are estimated by \ols. The benchmark model regresses $y_t$
on a constant, and the alternative regresses $y_t$ on a constant and
$z_{t-1}$.  We use both \poscw\ original statistic and the new
statistic to test the null that the benchmark model's innovation is an
\mds.\footnote{\citet{ClW:07} report the performance of the tests
  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
  based on the naive Gaussian statistic.}

\begin{table}[tb]
  \centering
  \input{tex/mc1}
  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
    and West's (2007) statistic rejects; Pr[new] shows the fraction of
    simulations for which this paper's test rejects; and Pr[disagree]
    gives the fraction of simulations in which this paper's test and
    Clark and West's (2007) give different conclusions.}
\label{tab:mc1}
\end{table}

The second \dgp\ is
\begin{align*}
  y_{t} &= 2.237 + 0.261 y_{t-1} + \gamma_{1} z_{t-1} + \gamma_{2}
  z_{t-2} + \gamma_{3} z_{t-3} + \gamma_{4} z_{t-4} + e_{t} \\
  z_{t} &= 0.804 z_{t-1} - 0.221 z_{t-2} + 0.226 z_{t-3} - 0.205
  z_{t-4} + v_{t} \nonumber \\
  \binom{e_{t}}{v_{t}} &\sim N\Bigg(
  \begin{pmatrix}
    0 \\ 0
  \end{pmatrix},
  \begin{pmatrix}
    10.505 & 1.036 \\ 1.036 & 0.366
  \end{pmatrix}
  \Bigg) \nonumber\\\nonumber
  \gamma &=
  \begin{cases}
    0 & \text{size simulations}\\
    (3.363, -0.633, -0.377, -0.529)' & \text{power simulations}.
  \end{cases}
\end{align*}
The benchmark model for $y_{t}$ is an AR(1) and the alternative model
includes all four lags of $z_{t}$.  For this simulation, $R$ is 80 or
120 and $P$ is 40, 80, 120, or 160.  \citet{ClW:07} argue that the
first \dgp\ mimics an asset pricing application and the second mimics
\gdp\ growth forecasting using the Federal Reserve Bank of Chicago's
National Activity Index.

\begin{table}[tb]
  \centering
  \input{tex/mc2}
  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
    and West's (2007) statistic rejects; Pr[new] shows the fraction of
    simulations for which this paper's test rejects; Pr[disagree] gives
    the fraction of simulations in which this paper's test and Clark and
    West's (2007) give different conclusions.}
\label{tab:mc2}
\end{table}

Table~\ref{tab:mc1} presents the simulation results for~\textsc{dgp}~1
and Table~\ref{tab:mc2} for~\textsc{dgp}~2.  For all of the stable
parameter values, the proposed new statistic has similar rejection
probability to \citepos{ClW:07}.  Clark and West's test is slightly
more undersized than the new test, but has a little higher power under
the alternative.  In general, the statistics perform similarly well.

For the simulations with a single break, the new statistic modestly
higher power than \poscw\ original test.  For most parametrizations of
\dgp\ 1, the new test rejects over 90\% of the time, while Clark and
West's test rejects about 40\% of the time.  So mixing window
strategies can give a small power advantage when testing for
time-varying predictability, and performs similarly to the original
test when testing for stable outperformance.

@@

This section demonstrates the use of our new statistics by revisiting
\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
that many variables thought to predict excess returns (measured as the
difference between the yearly log return of the S\&P 500 index and the
T-bill interest rate) on the basis of in-sample evidence fail to do so
out-of-sample.  To show this, Goyal and Welch look at the forecasting
performance of models using a lag of the variable of interest, and
show that these models do not significantly outperform the excess
return's recursive sample mean.

@@

\section{Conclusion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window---as do Clark and West---but estimating
the benchmark model with a recursive window.  Simulations indicate
that the new statistic behaves similarly to Clark and West's original
test when the \dgp\ is stable, suggesting that the new statistic is
a suitable replacement in applied research.  The paper also presents a
method for comparing the benchmark model to several alternative models
simultaneously and improves block bootstrap procedures of \oos\
statistics.

>>>>

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
\usepackage[T1]{fontenc}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round,comma]{natbib}
\usepackage[margin=1.25in]{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\onehalfspacing
\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/mcDef}
\input{tex/ap}

@@

The next section presents our new statistics and Section~\ref{sec:1b}
our block bootstrap result.  Section~\ref{sec:2} presents
simulations that compare our pairwise \oos\ test to \poscw\ original
statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability. Section~\ref{sec:4} concludes.

@@

\section{Monte Carlo Results}\label{sec:2}
This section presents Monte Carlo experiments demonstrating that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they study, but can
have substantially higher power when the \dgp\ has a structural
break.\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \textsc{MASS}
  \citep[7.3-22]{VeR:02}, xtable \citep[version 1.6-0]{Dah:09}, and
  dbframe \citep[version 0.2.7]{Cal:10b} packages.}

The \dgp\ has three different parametrizations: one to study the
tests' size, one to study power under stationarity, and one to study
power if there is a single break in the relationship between the
target and predictors.  The \dgp\ is:
\begin{align*}
  y_t &= \gamma_{1t} + \gamma_{2t} z_{t-1} + e_t &
  \gamma_t &=
  \begin{cases}
    (0.5, 0)    & \text{size simulations} \\
    (0.5, 0.35) & \text{power (stable)} \\
    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
  \end{cases}\\\nonumber
  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
  \end{pmatrix}
   , \begin{pmatrix} 18 & -
    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
\end{align*}
Both models are estimated by \ols. The benchmark model regresses $y_t$
on a constant, and the alternative regresses $y_t$ on a constant and
$z_{t-1}$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
pricing application similar to \citepos{GoW:08} which we study in
Section~\ref{sec:3}.

For comparison, we study this paper's new statistic as well as \poscw
rolling-window and recursive-window test statistics.  Clark and West
only prove that their rolling-window statistic is asymptotically
normal, and only then if the benchmark model is not estimated, but
their recursive-window statistic is popular in practice and in
simulations tends to perform similarly to their rolling window test.
We use all three of these statistics to test the null that the
benchmark model's innovation is an \mds.\footnote{\citet{ClW:07}
  report the performance of the tests proposed by \citet{CCS:01} and
  \citet{ClM:05} as well, and of tests based on the naive Gaussian
  statistic.}

\begin{table}[tb]
  \centering
  \input{tex/mc1}
  \caption{Size and power of the \oos\ tests in the simulations 
    described by Section~\ref{sec:2}, at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\textsc{cw} roll.] shows the fraction of simulations for
    which Clark and West's (2007) rolling-window statistic rejects; 
    Pr[\textsc{cw} rec.] shows the fraction of simulations for which 
    their recursive-window statistic rejects; and Pr[new] shows the fraction of
    simulations for which this paper's test rejects.}
\label{tab:mc1}
\end{table}

Table~\ref{tab:mc1} presents the simulation results.  For all of the
stable parameter values, the proposed new statistic has similar
rejection probability to \citepos{ClW:07}.  Both of Clark and West's
tests are generally slightly undersized relative to our new test,
which is itself slightly undersized: when $R$ is 120 and $P$ is 360
our test statistic has size 7.6\% and Clark and West's rolling and
recursive window tests have size 7.5\% and 6.2\% respectively, at a
nominal size of 10\%.  For the stable alternative, our new statistic
typically has slightly higher power than Clark and West's rolling
window and lower power than their recursive window.  For example, when
$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
our statistic at 73.0\%, and the recrusive window statistic at 82.3\%,
again for a nominal size of 10\%.  In general, the statistics perform
similarly under stability.

For the simulations with a single break, the new statistic has
considerably higher power than \poscw\ original tests across all of
the choices of $R$ and $P$; the rejection probability is more than
twice as large for most parametrizations.  When $R$ is 120 and $P$ is
360 with a nominal size of 10\%, for example, the new statistic
rejects at 96.4\% while the rolling and recursive window statistics
reject at 35.5\% and 32.9\% respectively.  Results for other choices
of nominal size and sample split give similar results.  So mixing
window strategies can give a large power advantage when testing for
time-varying predictability, and performs similarly to the original
test when testing for stable outperformance.

@@

This section demonstrates the use of our new statistic by revisiting
\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
that many variables thought to predict excess returns (measured as the
difference between the yearly log return of the S\&P 500 index and the
T-bill interest rate) on the basis of in-sample evidence fail to do so
out-of-sample.  To show this, Goyal and Welch look at the forecasting
performance of models using a lag of the variable of interest, and
show that these models do not significantly outperform the excess
return's recursive sample mean.

@@

\section{Conclusion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window---as do Clark and West---but estimating
the benchmark model with a recursive window.  Simulations indicate
that the new statistic behaves similarly to Clark and West's original
test when the \dgp\ is stable but can have much higher power when the 
\dgp\ has structural breaks.  The paper also presents a
method for comparing the benchmark model to several alternative models
simultaneously and improves block bootstrap procedures of \oos\
statistics.
